\section{Question}

\subsection{Now investigate the structure of the gene. Find the gene in a database. Which chromosome is it located on, and at which position along the chromosome?}

\textit{NCBI} page: \href{https://www.ncbi.nlm.nih.gov/gene/3064}{HTT huntingtin [ Homo sapiens (human) ]}

It is located in \textbf{Chromosome 4 - \textit{NC\_000004.12}}, from position \textit{3074510} to \textit{3243960}.

% - - - - - - - - - - - - - - - - - - - - - - - - - - -

\subsection{What is the structure of the gene, how many exons and introns does it have?}

It has \textbf{\textit{67} exons}, and therefore \textbf{\textit{66} introns} \textit{(67 - 1)}.

% - - - - - - - - - - - - - - - - - - - - - - - - - - -

\begin{center}
    \textcolor[RGB]{180,180,180}{\rule{\textwidth}{0.4pt}}
\end{center}

\large{\textbf{Download the gene transcript and the coding sequences for your gene - if multiple are listed, choose the main one, at the top of the list.}}

\subsection{Where did you get this sequence from and what was the unique identifier used so that someone else could be sure they were looking at the same sequence?}

I downloaded both the \textit{\textbf{Complete Record} FASTA} and \textit{\textbf{Coding Sequences} FASTA nucleotide} files from the \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_000004.12?report=fasta&from=3074510&to=3243960}{NCBI Gene DB}.

The sequence unique identifier is \textit{NC\_000004.12}, from	\textit{GRCh38.p7}.

% - - - - - - - - - - - - - - - - - - - - - - - - - - -

\subsection{How long is the transcript, and what proportion is coding?}

The \textit{Complete Record} file has a length of \textbf{171871} nucleotides. The \textit{Coding Sequences} file is \textbf{9563} nucleotides long. Therefore, we can say that only \textbf{5.56\%} of the entire gene correspond to coding sequences:

\[
\frac{9563}{171871} = 0.05564
\]

\newpage
